Analysis-ready VCF at Biobank scale using Zarr

### 2025-01-23 paper.tex
Update Jeremy's orcid and accents
Added Jonny Hancox to author list

% Middle, alphabetical order
\author[6]{Benjamin Elsworth} % https://orcid.org/0000-0001-7328-4233
\author[7,8]{Jeremy Guez} % ?
\author[9]{Ben Jeffery} % https://orcid.org/0000-0002-1982-6801
\author[7,8,10]{ Konrad J. Karczewski} % https://orcid.org/0000-0003-2878-4671
\author[11]{Alistair Miles} % https://orcid.org/0000-0001-9018-4680
\author[12]{Sam Tallman} % https://orcid.org/0000-0001-7183-6276
\author[13]{Per Unneberg} % https://orcid.org/0000-0001-5735-3315
\author[1]{Rafal Wojdyla} % https://orcid.org/0009-0005-0735-7090
\author[14]{Shadi Zabad} % https://orcid.org/0000-0002-8003-9284

% Senior 
\author[1,\authfn{2}]{Jeff Hammerbacher} % https://orcid.org/0000-0001-6596-8563
\author[9,\authfn{2},\authfn{3}]{Jerome Kelleher} % https://orcid.org/0000-0002-7894-5253

\affil[1]{Related Sciences}
\affil[2]{The New Zealand Institute for Plant \& Food Research Ltd, Lincoln,
New Zealand}
\affil[3]{Department of Biochemistry, School of Biomedical Sciences, University of Otago, Dunedin, New Zealand}
\affil[4]{Independent researcher}
\affil[5]{Tom White Consulting Ltd.}
\affil[6]{Our Future Health}
\affil[7]{Program in Medical and Population Genetics, Broad Institute of MIT and Harvard, Cambridge, Massachusetts 02142, USA}
\affil[8]{Analytic and Translational Genetics Unit, Massachusetts General
Hospital, Boston, Massachusetts 02114, USA}
\affil[9]{Big Data Institute, Li Ka Shing Centre for Health Information and Discovery, 
University of Oxford, UK}
\affil[10]{Analytic and Translational Genetics Unit, Massachusetts General
Hospital, Boston, Massachusetts 02114, USA}
\affil[11]{Wellcome Sanger Institute}
\affil[12]{Genomics England}
\affil[13]{Department of Cell and Molecular Biology, National
  Bioinformatics Infrastructure Sweden, Science for Life Laboratory,
  Uppsala University, Uppsala, Sweden}
\affil[14]{School of Computer Science, McGill University, Montreal, QC, Canada}

>>>>

% Middle, alphabetical order
\author[6]{Benjamin Elsworth} % https://orcid.org/0000-0001-7328-4233
\author[7,8]{Jérémy Guez} % https://orcid.org/0009-0007-6406-5187
\author[9]{Jonny Hancox} % ?
\author[10]{Ben Jeffery} % https://orcid.org/0000-0002-1982-6801
\author[7,8,11]{ Konrad J. Karczewski} % https://orcid.org/0000-0003-2878-4671
\author[12]{Alistair Miles} % https://orcid.org/0000-0001-9018-4680
\author[13]{Sam Tallman} % https://orcid.org/0000-0001-7183-6276
\author[14]{Per Unneberg} % https://orcid.org/0000-0001-5735-3315
\author[1]{Rafal Wojdyla} % https://orcid.org/0009-0005-0735-7090
\author[15]{Shadi Zabad} % https://orcid.org/0000-0002-8003-9284

% Senior 
\author[1,\authfn{2}]{Jeff Hammerbacher} % https://orcid.org/0000-0001-6596-8563
\author[10,\authfn{2},\authfn{3}]{Jerome Kelleher} % https://orcid.org/0000-0002-7894-5253

\affil[1]{Related Sciences}
\affil[2]{The New Zealand Institute for Plant \& Food Research Ltd, Lincoln,
New Zealand}
\affil[3]{Department of Biochemistry, School of Biomedical Sciences, University of Otago, Dunedin, New Zealand}
\affil[4]{Independent researcher}
\affil[5]{Tom White Consulting Ltd.}
\affil[6]{Our Future Health}
\affil[7]{Program in Medical and Population Genetics, Broad Institute of MIT and Harvard, Cambridge, Massachusetts 02142, USA}
\affil[8]{Analytic and Translational Genetics Unit, Massachusetts General
Hospital, Boston, Massachusetts 02114, USA}
\affil[9]{Nvidia}
\affil[10]{Big Data Institute, Li Ka Shing Centre for Health Information and Discovery, 
University of Oxford, UK}
\affil[11]{Novo Nordisk Foundation Center for Genomic Mechanisms of Disease, Broad Institute of MIT and Harvard, Cambridge, Massachusetts 02142, USA}
\affil[12]{Wellcome Sanger Institute}
\affil[13]{Genomics England}
\affil[14]{Department of Cell and Molecular Biology, National
  Bioinformatics Infrastructure Sweden, Science for Life Laboratory,
  Uppsala University, Uppsala, Sweden}
\affil[15]{School of Computer Science, McGill University, Montreal, QC, Canada}
